Tree size, exposure, and hydraulic traits interactively shape drought response in a temperate broadleaf forest

### 2019-06-29 manuscript/03-methods.Rmd
Update 03-methods.Rmd
update on hydraulic traits

Hydraulic traits were collected from SCBI and are summarized in Table 1. Ring porosity qualifications were obtained from [@andersonteixeira_size-related_2015].

Need to say the methodology for all traits used (**Nobby making short list**)
1. PLA
2. LMA
3. Chlorophyll
4. Wood density
5. TLP
6. P50 = psi_0.5_kl50
7. P80 = psi_0.5_kl80

*Table 1. Species analyzed here, listed in descending order of ANPP_stem. n cores and DBH range represented, and species traits* [this should combine the two remaining tables in this section]

>>>>

Hydraulic traits were collected from SCBI and are summarized in Table 1. In August 2018, we collected leaf samples from three individuals of each species ... (**Nobby's description of methods for the following**) 
1. PLA
2. LMA
4. Wood density
5. TLP
6. P50 = psi_0.5_kl50
7. P80 = psi_0.5_kl80

**Table 1. Species analyzed here, listed in descending order of ANPP_stem. n cores and DBH range represented, and species traits** [*This replaces/combines the two remaining tables in this section. Suggested columns, with those to include only if they fit in parentheses: species, (stems >=10 cm per ha in plot), (ANPP_stem), n cores, DBH range of cores, (n cores in each canopy position) species means for each trait]
